Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-18 lqg-strings.tex
Sketched and added to main document the new energy and wave equation in static+transverse gauge

>>>>

Using the static gauge $\tau = t$ and the transverse gauge with $\frac{\partial X}{\partial s} \cdot \frac{\partial X}{\partial t} = 0$, where $s$ is the length along the string parameter, we find that the new form for the conserved energy per infinitesimal piece of the string is the regular energy of the Nambu-Goto string times the correction factor
\begin{equation} \label{eqn:string-energy}
	E \diff \sigma = T \gamma _{v_{\perp}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \diff s ,
\end{equation}
and the form of the wave equation maintains it's shape as in
\begin{equation} \label{eqn:corrected-NG-wave-equation}
	\mu _{eff} \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial}{\partial s} \left[ T_{eff} \frac{\partial \Vec{X}}{\partial s} \right] = 0 ,
\end{equation}
where the effective mass density and effective tension are given by
\begin{align}
	\mu _{eff} & = \mu \gamma _{v_{\perp}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) \label{eqn:effective-mass}            \\
	T_{eff}    & = \frac{T}{\gamma _{v_{\perp}}} \left( 1 - \frac{g \Delta}{2 (- h)} \right) . \label{eqn:effective-tension}
\end{align}
